The dynamic stiffness matrix based on the extended separation-of-variables type solution for the free vibration of orthotropic rectangular thin plates

### 2025-05-16 Paper7.tex
some twist

Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the separation-of-variables (SOV) method, which provides concise and explicit eigensolutions.
The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
However, this SOV method is not suitable to deal with plates with free boundary conditions.
Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient was proposed to accommodate plates with all four classical boundary conditions, i.e., simply supported, clamped, guided, and free.
Based on the Rayleigh quotient model, alternative iterative and improved SOV methods have been subsequently proposed \cite{xing2020improved}.
Although SOV methods provide concise closed-form analytical solutions, they require solving a specific set of highly nonlinear eigenvalue equations for each type of boundary condition.
However, even when considering only the four classic homogeneous cases, it becomes evident that 55 different boundary condition combinations exist for a rectangular plate, making the process tedious.

@@

\FloatBarrier
\section{Mathematical model}\label{sec:Mathematical model}
\begin{figure}[!htbp]
	\centering
	\resizebox{0.8\textwidth}{!}
	{
		\input{figs/general_plate_tikz.tex}
	}
	\caption{\small The orthotropic rectangular plate with all edges elastically restrained.} 
	\label{fig:platemode}
\end{figure}
Consider a thin orthotropic rectangular plate of length \(2a\) and width \(2b\), with all four edges restrained by vertical translational springs \(k^v\) and rotational springs \(k^r\), as shown in \Cref{fig:platemode}. 
The coordinate origin is located at the center of the plate.

The governing differential equation for the free vibration of a thin orthotropic plate is given by \citep{xing2020improved}:  
%
\begin{equation}\label{eq:governing_EOM}
	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\alpha^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\alpha^4\frac{\partial^4w}{\partial \eta^4} = \rho h\alpha^4\omega^2w,
\end{equation}
%
where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates,
and the bending stiffness parameters are defined as:
%
\begin{equation}\label{eq:bd_stiff}
	\begin{split}
		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \quad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
		&D_{66} = \frac{G_{12}h^3}{12}, \quad D_{12} = v_{12}D_{22} = v_{21}D_{11}, \quad D_3 = D_{12} + 2D_{66},
	\end{split}
\end{equation}
%
where \(\rho\) and \(h\) denote the mass density and thickness of the plate, respectively; \(E_1\) and \(E_2\) are the Young’s moduli in the \(x\)- and \(y\)-directions, respectively; \(G_{12}\) is the shear modulus, and \(v_{12}\) and \(v_{21}\) are the Poisson’s ratios.

Instead of solving the free vibration of the thin orthotropic plate using \Cref{eq:governing_EOM}, it is suggested that the vibration of the thin plate can also be solved using the Rayleigh quotient variational principle \cite{xing2018overall}:
%
\begin{equation}\label{eq:Rayleigh}
	\begin{split}
		\delta U_{mag} &= \omega^2\,\delta T_0,
	\end{split}
\end{equation}
%
where \(\delta\) denotes variation, \(U_{mag}\) is the magnitude of the potential energy of the plate, and \(\omega^2 T_0\) represents the magnitude of the kinetic energy of the plate.
The potential energy of the plate can be expressed as \cite{xing2020extended}:
%
\begin{equation}\label{eq:poten_energy}
	\begin{split}
		U^{I} &= \frac{1}{2}\iint \Big[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Big] \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}
%
And the kinetic energy is:
%
\begin{equation}\label{eq:kine_energy}
	\begin{split}
		T &= \frac{1}{2}\iint \rho h \left(\frac{\partial W}{\partial t}\right)^2 \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}

Assuming the solution of the deflection \( W(x, y; t) = w(x, y) e^{i \omega t} \) for harmonic plate motion, 
where \( \ii = \sqrt{-1} \), \( w(x, y) \) is the mode shape, and \( \omega \) is the radial frequency.  
By substituting \( W(x, y; t) = w(x, y) e^{i \omega t} \) into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
The separable form of the mode shape function \( w(\xi, \eta) \) is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where \( \phi(\xi) \) and \( \psi(\eta) \) can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

@@

Supposing the edges of the plate in both the \(x\)- and \(y\)-directions are elastically restrained by homogeneous vertical translational and rotational springs.
The vertical translational and rotational springs at the \(\xi = -1\) end are defined as \(k^v_{\xi = -1}\) and \(k^r_{\xi = -1}\), respectively, and at the \(\xi = 1\) end as \(k^v_{\xi = 1}\) and \(k^r_{\xi = 1}\), respectively. 
Thus, the potential energy along the supported edge in the \(x\)-direction can be expressed by:

@@

		&\quad +  \int\left[k^r_{\xi=1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=1} \left( W \right)^2\right]_{x=a} \id y.

@@

From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the \(x\)-direction is obtained as:

@@

		&\quad + ab \int\left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2\right]_{\xi=1} \, \id \eta.

@@

The magnitude of potential energy of the plate in the \(x\)-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:

@@

		&\quad \left.  + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\
		&\quad  + ab \int \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2 \right]_{\xi=-1} \, \id \eta

@@

		&\quad \left. + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\quad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},

@@

By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:

@@

By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yields:

@@

		&\quad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
		&\quad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 

@@

		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 

@@

		&\quad + \bigg( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 

@@

		&\quad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 

@@

Thus, the governing differential equation in the \( x \)-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:

@@

where \(\Omega_x = \sqrt[4]{\omega_x^2 \rho h / D_{11}}\).
By substituting \(\phi(\xi) = A e^{\mu \xi}\) into \Cref{eq:ODEx}, yields:

@@

The solution for \(\mu\) can be expressed as:

@@

The boundary conditions along the edges in the \(x\)-direction can be obtained from the remaining \(\delta \phi\) and \(\delta \frac{\id \phi}{\id \xi}\) parts in \Cref{eq:Rayleighx2}. 
The shear force equilibrium can be obtained from the \(\delta \phi\) part:

@@

		&\quad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}

@@

and from the \(\delta \frac{\id \phi}{\id \xi}\) part, the bending moment equilibrium:

@@

		&+ \frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.

@@

Thus, we can obtain the shear force and bending moment equilibrium along the edges \(\xi = -1\) and \(\xi = 1\) from \Cref{eq:inertial_forcex,eq:inertial_forcex2}, respectively, as:

@@

Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting \( k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} \), \( k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} \), \( S_{\alpha_1}=\sin\alpha_1  \), \( C_{\alpha_1}=\cos\alpha_1 \), \( Sh_{\alpha_1}=\sinh\alpha_1 \), \( Ch_{\alpha_1}=\cosh\alpha_1  \), \(S_{\beta_1}= \sin\beta_1 \), \( C_{\beta_1}=\cos\beta_1 \), \( Sh_{\beta_1}=\sinh\beta_1  \), and \(  Ch_{\beta_1}=\cosh\beta_1 \), we have:

@@

\subsection{Dynamic stiffness matrix corresponding to \(\omega_y\)}\label{sec:DSMy}
In this section, the mode shape \(\phi(\xi)\) derived in \(\Cref{sec:DSMx}\) is utilized to obtain the dynamic stiffness matrix in the \(y\)-direction.  
The vertical translational and rotational springs at \(\eta = -1\) are denoted as \(k^v_{\eta = -1}\) and \(k^r_{\eta = -1}\), respectively, while those at \(\eta = 1\) are represented by \(k^v_{\eta = 1}\) and \(k^r_{\eta = 1}\).

The magnitude of total potential energy along the edges in the \( y \)-direction is given by:  

@@

		&\quad + ab \int \left[ \frac{k^r_{\eta=1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{a} w^2 \right]_{\eta=1} \id \xi.  

@@

The magnitude of potential energy of the plate in the \(y\)-direction can be obtained from

@@

		&\quad \left.  + \frac{4 D_{66}}{a^2 b^2}\left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta+ab \int \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{b} \left( w \right)^2 \right]_{\eta=1} \id\xi\\
		&\quad+ab \int \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{b} \left( w \right)^2 \right]_{\eta=-1} \id\xi.

@@

		&\quad \left. + \frac{4D_{66}}{a^2b^2} J_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + abJ_1 \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2

@@

		&\quad + abJ_1 \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2

@@

The coefficient \( T_0 \) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:

@@

By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving \( \delta \psi \) and \( \delta\frac{\id \psi}{\id \eta} \) in \Cref{eq:Rayleighy} by variation calculus, yields:

@@

		&\quad \left. + \left( \frac{D_{11}}{a^4} J_4 - \omega_y^2 \rho h J_1 \right) \psi \right] \delta \psi \, \id\eta \\
		&\quad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi \delta \psi)_{\eta=-1} 

@@

		&\quad + \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 

@@

		&\quad + \left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 

@@

		&\quad + \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 

@@

Thus, the governing differential equation in the \( y \)-direction can be obtained from the integration part in \Cref{eq:Rayleighy2}:

@@

where \( \Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}} \).
By substituting \( \psi(\eta) = B e^{\lambda \eta} \) into \Cref{eq:ODEy}, yields:

@@

The solution for \( \lambda \) can be expressed as:

@@

The boundary conditions along the edges in the \( y \)-direction can be obtained from the remaining \( \delta \psi \) and \( \delta \frac{\id \psi}{\id \eta} \) parts in \Cref{eq:Rayleighy2}. 
The shear force equilibrium can be obtained from the \( \delta \psi \) part:

@@

		&\quad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} J_1 (\psi )_{\eta=1} = 0,

@@

and from the \( \delta \frac{\id \psi}{\id \eta} \) part, the bending moment equilibrium:

@@

 	&+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.

@@

\( k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} \), 

>>>>

Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the SOV method, which provides concise and explicit eigensolutions.
The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
However, this SOV method is not suitable to deal with plates with free boundary conditions.
Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient was proposed to accommodate plates with all four classical boundary conditions, i.e., simply supported, clamped, guided, and free.
Based on the Rayleigh quotient model, alternative iterative and improved SOV methods have been subsequently proposed \cite{xing2020improved}.
Although SOV methods provide concise closed-form analytical solutions, they require solving a specific set of highly nonlinear eigenvalue equations for each type of boundary condition.
However, even when considering only the four classic homogeneous cases, it becomes evident that 55 different boundary condition combinations exist for a rectangular plate, making the process tedious.

@@

\FloatBarrier
\section{Mathematical model}\label{sec:Mathematical model}
\begin{figure}[!htbp]
	\centering
	\resizebox{0.8\textwidth}{!}
	{
		\input{figs/general_plate_tikz.tex}
	}
	\caption{\small The orthotropic rectangular plate with all edges elastically restrained.} 
	\label{fig:platemode}
\end{figure}
Consider a thin orthotropic rectangular plate of length $2a$ and width $2b$, with all four edges restrained by vertical translational springs $k^v$ and rotational springs $k^r$, as shown in \Cref{fig:platemode}. 
The coordinate origin is located at the center of the plate.

The governing differential equation for the free vibration of a thin orthotropic plate is given by \citep{xing2020improved}:  
%
\begin{equation}\label{eq:governing_EOM}
	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\alpha^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\alpha^4\frac{\partial^4w}{\partial \eta^4} = \rho h\alpha^4\omega^2w,
\end{equation}
%
where $ \alpha = a / b $ is the aspect ratio; $ \xi = x / a $ and $ \eta = y / b $ are the normalized coordinates,
and the bending stiffness parameters are defined as:
%
\begin{equation}\label{eq:bd_stiff}
	\begin{split}
		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \qquad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
		&D_{66} = \frac{G_{12}h^3}{12}, \quad D_{12} = v_{12}D_{22} = v_{21}D_{11}, \quad D_3 = D_{12} + 2D_{66},
	\end{split}
\end{equation}
%
where $\rho$ and $h$ denote the mass density and thickness of the plate, respectively; $E_1$ and $E_2$ are the Young’s moduli in the $x$- and $y$-directions, respectively; $G_{12}$ is the shear modulus, and $v_{12}$ and $v_{21}$ are the Poisson’s ratios.

Instead of solving the free vibration of the thin orthotropic plate using \Cref{eq:governing_EOM}, it is suggested that the vibration of the thin plate can also be solved using the Rayleigh quotient variational principle \cite{xing2018overall}:
%
\begin{equation}\label{eq:Rayleigh}
	\begin{split}
		\delta U_{mag} &= \omega^2\,\delta T_0,
	\end{split}
\end{equation}
%
where $\delta$ denotes variation, $U_{mag}$ is the magnitude of the potential energy of the plate, and $\omega^2 T_0$ represents the magnitude of the kinetic energy of the plate.
The potential energy of the plate can be expressed as \cite{xing2020extended}:
%
\begin{equation}\label{eq:poten_energy}
	\begin{split}
		U^{I} &= \frac{1}{2}\iint \Big[D_{11}\left(\frac{\partial^2 W}{\partial x^2}\right)^2 + 2D_{12}\frac{\partial^2 W}{\partial x^2}\frac{\partial^2 W}{\partial y^2} + D_{22}\left(\frac{\partial^2 W}{\partial y^2}\right)^2 \\
		&\qquad + 4D_{66}\left(\frac{\partial^2 W}{\partial x \partial y}\right)^2\Big] \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}
%
And the kinetic energy is:
%
\begin{equation}\label{eq:kine_energy}
	\begin{split}
		T &= \frac{1}{2}\iint \rho h \left(\frac{\partial W}{\partial t}\right)^2 \, \mathrm{d}x \, \mathrm{d}y.
	\end{split}
\end{equation}

Assuming the solution of the deflection $ W(x, y; t) = w(x, y) e^{i \omega t} $ for harmonic plate motion, 
where $ \ii = \sqrt{-1} $, $ w(x, y) $ is the mode shape, and $ \omega $ is the radial frequency.  
By substituting $ W(x, y; t) = w(x, y) e^{i \omega t} $ into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
The separable form of the mode shape function $ w(\xi, \eta)$ is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where $ \phi(\xi) $ and $\psi(\eta) $ can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

@@

Supposing the edges of the plate in both the $x$- and $y$-directions are elastically restrained by homogeneous vertical translational and rotational springs.
The vertical translational and rotational springs at the $\xi = -1$ end are defined as $k^v_{\xi = -1}$ and $k^r_{\xi = -1}$, respectively, and at the $\xi = 1$ end as $k^v_{\xi = 1}$ and $k^r_{\xi = 1}$, respectively. 
Thus, the potential energy along the supported edge in the $x$-direction can be expressed by:

@@

		&\qquad +  \int\left[k^r_{\xi=1} \left( \frac{\partial W}{\partial x} \right)^2 + k^v_{\xi=1} \left( W \right)^2\right]_{x=a} \id y.

@@

From \Cref{eq:poten_energy_edgex}, the magnitude of total potential energy along the edges in the $x$-direction is obtained as:

@@

		&\qquad + ab \int\left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2\right]_{\xi=1} \, \id \eta.

@@

The magnitude of potential energy of the plate in the $x$-direction can be obtained from \Cref{eq:poten_energy_mag,eq:poten_energy_edgex2} as:

@@

		&\qquad \left.  + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta + ab \int \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=1}}{a} \left( w \right)^2 \right]_{\xi=1} \, \id \eta \\
		&\qquad  + ab \int \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\partial w}{\partial \xi} \right)^2 + \frac{k^v_{\xi=-1}}{a} \left( w \right)^2 \right]_{\xi=-1} \, \id \eta

@@

		&\qquad \left. + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\qquad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},

@@

By taking \Cref{eq:displace_func} into account, the coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:

@@

By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving $\delta \phi$ and $\delta\frac{\id  \phi}{\id \xi}$ in \Cref{eq:Rayleighx} by variation calculus, yields:

@@

		&\qquad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
		&\qquad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 

@@

		&\qquad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 

@@

		&\qquad + \bigg( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 

@@

		&\qquad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 

@@

Thus, the governing differential equation in the $ x $-direction can be obtained from the integration part in \Cref{eq:Rayleighx2}:

@@

where $\Omega_x = \sqrt[4]{\omega_x^2 \rho h / D_{11}}$.
By substituting $\phi(\xi) = A e^{\mu \xi}$ into \Cref{eq:ODEx}, yields:

@@

The solution for $\mu$ can be expressed as:

@@

The boundary conditions along the edges in the $x$-direction can be obtained from the remaining $\delta \phi$ and $\delta \frac{\id \phi}{\id \xi}$ parts in \Cref{eq:Rayleighx2}. 
The shear force equilibrium can be obtained from the $\delta \phi$ part:

@@

		&\qquad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}

@@

and from the $\delta \frac{\id \phi}{\id \xi}$ part, the bending moment equilibrium:

@@

		& \qquad\frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.

@@

Thus, we can obtain the shear force and bending moment equilibrium along the edges $\xi = -1$ and $\xi = 1$ from \Cref{eq:inertial_forcex,eq:inertial_forcex2}, respectively, as:

@@

Substituting \Cref{eq:phi_solution1} into \Cref{eq:boundaryx}, and denoting $ k^{v*}_{\xi} = \frac{2a^3 k^v_{\xi}}{D_{11}} $, $ k^{r*}_{\xi} = \frac{2a k^r_{\xi}}{D_{11}} $, $ S_{\alpha_1}=\sin\alpha_1 $, $ C_{\alpha_1}=\cos\alpha_1 $, $ Sh_{\alpha_1}=\sinh\alpha_1 $, $ Ch_{\alpha_1}=\cosh\alpha_1 $, $S_{\beta_1}= \sin\beta_1 $, $C_{\beta_1}=\cos\beta_1$, $Sh_{\beta_1}=\sinh\beta_1 $, and $  Ch_{\beta_1}=\cosh\beta_1 $, we have:

@@

\subsection{Dynamic stiffness matrix corresponding to $\omega_y$}\label{sec:DSMy}
In this section, the mode shape $\phi(\xi)$ derived in $\Cref{sec:DSMx}$ is utilized to obtain the dynamic stiffness matrix in the $y$-direction.  
The vertical translational and rotational springs at $\eta = -1$ are denoted as $k^v_{\eta = -1}$ and $k^r_{\eta = -1}$, respectively, while those at $\eta = 1$ are represented by $k^v_{\eta = 1}$ and $k^r_{\eta = 1}$.

The magnitude of total potential energy along the edges in the $y$-direction is given by:  

@@

		&\qquad + ab \int \left[ \frac{k^r_{\eta=1}}{a^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{a} w^2 \right]_{\eta=1} \id \xi.  

@@

The magnitude of potential energy of the plate in the $y$-direction can be obtained from

@@

		&\qquad \left.  + \frac{4 D_{66}}{a^2 b^2}\left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \id\xi \, \id\eta+ab \int \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=1}}{b} \left( w \right)^2 \right]_{\eta=1} \id\xi\\
		&\qquad+ab \int \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\partial w}{\partial \eta} \right)^2 + \frac{k^v_{\eta=-1}}{b} \left( w \right)^2 \right]_{\eta=-1} \id\xi.

@@

		&\qquad \left. + \frac{4D_{66}}{a^2b^2} J_3 \left(\frac{\id \psi }{\id \eta} \right)^2 \right] \, \id\eta  + abJ_1 \left[ \frac{k^r_{\eta=1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2

@@

		&\qquad + abJ_1 \left[ \frac{k^r_{\eta=-1}}{b^3} \left( \frac{\id \psi}{\id \eta} \right)^2

@@

The coefficient $T_0$ of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:

@@

By substituting \Cref{eq:poten_energy_toly2,eq:kine_energyy} into \Cref{eq:Rayleighy}, and relieving $ \delta \psi $ and $\delta\frac{\id \psi}{\id \eta}$ in \Cref{eq:Rayleighy} by variation calculus, yields:

@@

		&\qquad \left. + \left( \frac{D_{11}}{a^4} J_4 - \omega_y^2 \rho h J_1 \right) \psi \right] \delta \psi \, \id\eta \\
		&\qquad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi \delta \psi)_{\eta=-1} 

@@

		&\qquad + \left[ \left( \frac{4D_{66}}{a^2b^2} J_3 - \frac{D_{12}}{a^2b^2} J_2 \right) \frac{\id \psi}{\id \eta} 

@@

		&\qquad + \left( \frac{D_{12}}{a^2b^2} J_2 \psi + \frac{D_{22}}{b^4} J_1 \frac{\id^2 \psi}{\id \eta^2} \right) 

@@

		&\qquad + \frac{2k^r_{\eta=-1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \delta\frac{\id \psi}{\id \eta} \right)_{\eta=-1} 

@@

Thus, the governing differential equation in the $y$-direction can be obtained from the integration part in \Cref{eq:Rayleighy2}:

@@

where $\Omega_y = \sqrt[4]{{\omega_y^2 \rho h}/D_{11}}$.
By substituting $\psi(\eta) = B e^{\lambda \eta}$ into \Cref{eq:ODEy}, yields:

@@

The solution for $\lambda$ can be expressed as:

@@

The boundary conditions along the edges in the $y$-direction can be obtained from the remaining $\delta \psi$ and $\delta \frac{\id \psi}{\id \eta}$ parts in \Cref{eq:Rayleighy2}. 
The shear force equilibrium can be obtained from the $\delta \psi$ part:

@@

		&\qquad + \frac{2k^v_{\eta=-1}}{b} J_1 (\psi )_{\eta=-1} + \frac{2k^v_{\eta=1}}{b} J_1 (\psi )_{\eta=1} = 0,

@@

and from the $\delta \frac{\id \psi}{\id \eta}$ part, the bending moment equilibrium:

@@

 	&\qquad+ \frac{2k^r_{\eta=1}}{b^3} J_1 \left( \frac{\id \psi}{\id \eta} \right)_{\eta=1}=0.

@@

$k^{v*}_{\eta} = \frac{2b^3 k^v_{\eta}}{D_{22}} $, 
